%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% acknowledge.tex: Acknowledgements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

I like to thank my advisor, David J. Lilja, who has suffered through more than a handful insensible ideas and lack of experience. Also members of ARCTiC lab, Biplob Debnath, Shruti Patil, Eric Seppanen, Weijun Xiao, Peng Li and William Tuohy for their friendship and insights. 

My thanks also goes to student members of CRIS, Weiping He, Anna Kryzhnyaya, Muthukumar Murugan, Joe Naps, Dongchul Park and Guanlin Lu for interesting projects and fun trips. 

I would also like to thank my committee members, David Du, Ulya Karpuzcu and John Sartori for their valuable comments and guidance. 
 
I would like to thank Jerry Fredin of NetApp for his support during the data deduplication project. 
I also like to thank Philip Shilain and Fred Douglis of EMC for their feedbacks on numerous projects. 
I would like to thank Dave B. Anderson and Luke W. Friendshuh for their support during the IO workload characterization project.
I would also like to thank Irfan Ahmed and DRS team at VMware for their support during the Romano project. 

I would like to thank DARPA, NSF and CRIS member companies for funding my projects as well as Minnesota Supercomputing Institute for providing the valuable compute cycles. 

I would also like to mention Sungwook and Sangyeon Jeong whom I promised to include in my acknowledgement in exchange for occasional free lunch at their place. 

I could not have survived long years of graduate school without the support of my parents whose interest in technology and willingness to invest in my education allowed me to find and pursue my passion. 

Although mostly distraction then help, I would also like to thank my brother, Nohguen, for the occasional fun times we were able to have in last 6 years. 

My special thanks goes to Hyewon and Ciana. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
